Proposed Solution

### 2016-11-14 Ennan-Proposal/travis.tex
Grammar in Travis

TravisCI~\cite{API} is a popular integration and build testing service 
connected to Github. It has been used on more than 17 
millions of projects. 
TravisCI allows programmers to automatically run their test suite on a fresh virtual machine every time they commit their code.
A TravisCI user must add a configuration file to the repository that specifies build conditions, 
such as which dependencies are required, and a set of benchmarks to test. 
The results of these tests (indicating either passing, failing, or misconfiguration) 
are saved by TravisCI on a publicly available database~\cite{API}.

TravisCI misconfigurations are important to detect and correct before execution,
because any failed compilation can costs developer significant amount 
of time. A misconfiguration can cause a test suite to run up to 20 
minutes, only to report that the whole computation failed~\cite{API}.
If developer would have this information prior to the compilation attempt, they could
 identifying and correct potential misconfigurations.

A new challenge here is that we need to reason about a 
temporal component too. Having an entire TravisCI log for a given
project we can examine the sequence of changes of a configuration file
and we can detect what has changed so that we switched from a failing 
compilation to successful compilation.

@@

We then create a conjunction of \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} with
conjunctions and invoke an SMT solver to find a model for that formula.
The resulting model will define sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
Since we used a similar model to \app, we will still be able to provide justifications for the classification results.

>>>>

TravisCI~\cite{API} is a popular integration and build testing service 
connected to Github. It has been used on more than 17 
million projects. 
TravisCI allows programmers to automatically run their test suite on a fresh virtual machine every time they commit their code.
A TravisCI user must add a configuration file to the repository that specifies build conditions, 
such as which dependencies are required, and a set of benchmarks to test. 
The results of these tests (indicating either passing, failing, or misconfiguration) 
are saved by TravisCI on a publicly available database~\cite{API}.

TravisCI misconfigurations are important to detect and correct before execution,
because any failed compilation can costs developer significant amount 
of time. A misconfiguration can cause a test suite to run up to 20 
minutes, only to report that the whole computation failed~\cite{API}.
If a developer had this information prior to the compilation attempt, they could
 identifying and correct potential misconfigurations.

A new challenge here is that we need to reason about a 
temporal component too. Having an entire TravisCI log for a given
project we can examine the sequence of changes of a configuration file
and detect what has changed, so that we switched from a failing 
compilation to successful compilation.

@@

We then create a conjunction of \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} and invoke an SMT solver to find a model for that formula.
The resulting model will define sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
Since we used a similar model to \app, we will still be able to provide justifications for the classification results.
